Assessing methods to adjust for assay differences across COVID-19 serological surveillance studies in Canada

### 2024-01-08 5_manuscript/manuscript.qmd
add more details in methods

```{r}
# Load a sample dataset
df_samp <- read_excel("../1_data/tables.xlsx", sheet = "sample")
```

@@

@@

To evaluate the severity of Covid-19 pandemic overtime in Alberta province, first we calculated the anti-N assay test positivity. Then, to bridge the gap between test positivity and population-level seroprevalence, we employed the Rogen-Gladen (RG) equation and Bayesian models. Following seroprevalence estimation, we further estimated the attack rate while adjusting for waning immunity. These estimations are dessignated to answer what proportion of the Alberta population that has been infected by SARS-CoV-2. We presented both seroprevalence and attack rate in a unified graph (**Fig**. X), displaying changes over time on a monthly scale.

@@

>>>>

```{r}
# Load a sample dataset
df_samp <- read_excel("../1_data/tables.xlsx", sheet = "sample")
df_dataset <- read_excel("../1_data/tables.xlsx", sheet = "dataset")
```

@@

(beware of the period of data collection for each dataset)

@@

To evaluate the severity of Covid-19 pandemic overtime in Alberta province, first we calculated the anti-N assay test positivity. Then, to bridge the gap between test positivity and population-level seroprevalence, we employed the Rogen-Gladen (RG) equation and Bayesian models. Following seroprevalence estimation, we further estimated the attack rate while adjusting for waning immunity using Bayesian models. These estimations are dessignated to answer what proportion of the target population that has been infected by SARS-CoV-2. We presented both seroprevalence and attack rate in a unified graph (**Fig**. X), displaying changes over time on a monthly scale.

Rogan Gladen equation:

$$
Prevalence = \frac{TestPositivity + (Spec-1)}{Spec + (Sens-1))}
$$

@@

t_samp
```

Table 2 Caption Here
```{r}
t_dataset<-as_flextable(df_dataset)
t_dataset <- fontsize(t_dataset, size = 10, part = "all")
t_dataset <- font(t_dataset, fontname = "Times", part = "all")
t_dataset <- theme_box(t_dataset)
t_dataset <- bg(t_dataset, bg = "#EAEAEA", part = "header")
t_dataset <- width(t_dataset, 1, 1.7)
t_dataset <- bg(t_dataset, i = c(1, 4), bg = "#DDDDDD", part = "body")
t_dataset <- bold(t_dataset, i = c(1, 4), part = "body")
t_dataset <- align(t_dataset, align = "left", part = "all")

t_dataset
```

:::
